%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% Modified by Dash Skndash S
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\projectentry}[4][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

% preamble
\firstname{Dash Skndash}
\familyname{S}
\address{Tamil Nadu, India}{}

% document
\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C C}
    \emailsymbol\enspace \emaillink{dashskndash@gmail.com} & \mobilephonesymbol\enspace +91 94889 18708 & \faLinkedin\enspace \href{https://www.linkedin.com/in/XXXXXX/}{linkedin @skndash96} & \faGithub\enspace
    \href{https://github.com/skndash96}{github @skndash96}
\end{tabularx}
\vspace{-2.0mm}

% LEFT COLUMN
\begin{minipage}[t]{0.62\textwidth}

\section{WORK EXPERIENCE}

\experienceentry{Delta Force}{Software Developer}{Aug 2025 -- Present}{On-site}
\begin{itemize}
    \item Managed Linux-based infrastructure for containerized services using Docker.
    \item Configured and maintained Nginx for reverse proxying, SSL termination, and routing.
    \item Performed deployments, monitoring, and production debugging via Linux CLI and logs.
\end{itemize}

\vspace{2.0mm}

\experienceentry{Orientation '25}{WebOps Manager}{2025}{Jul 2025 -- Sep 2025}
\begin{itemize}
    \item Led development of the official Orientation ’25 web platform using Payload CMS.
    \item Built internal tools including an attendance tracking system and a React Native app for operations.
    \item Delivered a polished frontend experience using GSAP-based animations and optimized UI flows.
\end{itemize}

\vspace{2.0mm}

\experienceentry{My Almamater}{Web Development Lead}{Feb 2024 -- Dec 2024}{Remote}
\begin{itemize}
    \item Built and scaled a student-run platform supporting print services, ride sharing, marketplace, and food ordering.
    \item Developed the application using Next.js with ISR and caching for performance and cost efficiency.
    \item Supported 2000+ monthly users with over 50k total page views under peak campus usage.
\end{itemize}

\section{PROJECTS}

\projectentry{Ocean Master}{Pragyan Games}{Dec 2025 -- Present}
\begin{itemize}
    \item Built a Go-based code runner and simulation pipeline for competitive game matches.
    \item Designed an asynchronous worker-based system to schedule and process matches.
    \item Executed untrusted user code securely using nsjail with stdin/stdout IPC.
\end{itemize}

\vspace{2.0mm}

\projectentry{Custom E-commerce Platform}{Full-stack Project}{Nov 2024}
\begin{itemize}
    \item Designed and implemented a multi-service e-commerce backend with production deployment.
    \item Built a headless commerce stack using Medusa, PostgreSQL, Redis, Meilisearch, and Nginx.
    \item Deployed and maintained the system on a self-managed VPS with caching and search optimization.
\end{itemize}

\end{minipage}
\hfill
% RIGHT COLUMN
\begin{minipage}[t]{0.35\textwidth}

\section{SUMMARY}
Second-year undergraduate Software Engineer Intern candidate with strong foundations in data structures, operating systems, and backend development. Hands-on experience building containerized services, Linux-based infrastructure, and scalable web systems using Go and JavaScript. Learns quickly and writes clean, maintainable code in collaborative environments.

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
Languages & Go, TypeScript, Python \\
Systems & Linux, Docker, Nginx \\
Frameworks & React, Next.js, React Native \\
Databases & PostgreSQL, Redis \\
Web \& APIs & REST APIs, WebSockets, JSON \\
Dev Practices & Git, Bash, CI/CD basics \\
Concepts & Data Structures, Concurrency, IPC \\
\end{tabularx}

\section{EDUCATION}
\educationentry{Bachelor of Technology (B.Tech.)}{NIT Trichy}{Tamil Nadu, India}
Expected May 2028

\section{LANGUAGES}
\begin{itemize}
    \item English (Advanced)
    \item Tamil (Native)
    \item Kannada (Native)
    \item Hindi (Beginner)
\end{itemize}

\section{INTERESTS}
\begin{itemize}
    \item Backend Systems and Infrastructure
    \item Competitive Programming
    \item Movies \& TV Shows
\end{itemize}

\end{minipage}

\end{document}
